Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-22 Draft.Rmd
Update Draft.Rmd

## Models 
```{r Lin Regr.}
model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

@@

```{r Linear Regression}
set.seed(123)
# Create the recipe for all models
rec <- train %>% 
    recipe(value ~ )

>>>>

## Models 
```{r Lin Regr. DELETE}
model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

@@

```{r Linear Regression KEEP}
set.seed(123)
# Create the recipe for all models
rec <- train %>% 
    recipe(value ~ )
